Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-11-19 large_number_squeezing_with_atoms.tex
Making it compile

\begin{abstract}
We examine the feasibility of creating and measuring large relative number squeezing in multicomponent trapped Bose-Einstein condensates.  In the absence of multimode effects, this squeezing can be arbitrarily large, but a range of processes limit the measurable squeezing in realistic trap configurations.  We conclude that high levels of squeezing with large numbers of atoms can only be achieved in one-dimensional traps with very even density profiles.
\end{abstract}

@@

The two-mode model suggests that arbitrarily high squeezing can be achieved using the intrinsic nonlinearities in a BEC, but it ignores the existence of multiple spatial modes.  The non-zero spatial dimensionality causes issues even when the modes do not interact.  A brief inspection of the two-mode model shows that the wait time for optimal squeezing is highly number dependent.  In a multimode environment, this means that the optimal wait time will be density-dependent.  Furthermore, the phases of areas with different density will evolve at different rates, so there will be poor mode matching when recombining a field with significant density variation.

@@

\section{Using a $\pi$ pulse to improve mode-matching
\begin{itemize}
  \item Say we can use a pi pulse to swap the populations half way through, so if the states have different nonlinearities we still end up with the same mode shapes when we recombine. The fact that this works will be clear from the SM equations for a(t), b(t) when the beam splitter is on
  \item show some plots of squeezing with and without the pi pulse
\end{itemize}

>>>>

\begin{abstract}
We examine the feasibility of creating and measuring large relative number squeezing in multicomponent trapped Bose-Einstein condensates.  In the absence of multimode effects, this squeezing can be arbitrarily large, but a range of processes limit the measurable squeezing in realistic trap configurations.  We conclude that high levels of squeezing with large numbers of atoms can only be achieved in one-dimensional traps with very even density profiles.  We introduce a method of maximising the measurable squeezing by using a pi-pulse during the process to improve spatial mode-matching.
\end{abstract}

@@

The two-mode model suggests that arbitrarily high squeezing can be achieved using the intrinsic nonlinearities in a BEC, but it ignores the existence of multiple spatial modes.  The non-zero spatial dimensionality causes issues even when the modes do not interact.  A brief inspection of the two-mode model shows that the wait time for optimal squeezing is highly number dependent.  In a multimode environment, this means that the optimal wait time will be density-dependent.  Furthermore, the phases of areas with different density will evolve at different rates, so there will be poor mode-matching when recombining a field with significant density variation.

@@

\section{Using a $\pi$ pulse to improve mode-matching}
\begin{itemize}
  \item Say we can use a pi pulse to swap the populations half way through, so if the states have different nonlinearities we still end up with the same mode shapes when we recombine. The fact that this works will be clear from the SM equations for a(t), b(t) when the beam splitter is on
  \item show some plots of squeezing with and without the pi pulse
\end{itemize}
